Integer Programming on Ising Spin-Glass

### 2020-09-14 paper/main.tex
Added back in accidentally removed section

As this mapping comes with a tunable parameter, such constraints can be lifted in a problem-specific manner to extend the applicability (Sec.~\ref{sec:methods:ILP-on-DWave}).
Furthermore, the same algorithm can be extended to quadratic constraint optimization problems (Sec.~\ref{sec:methods:ilp:quadratic}).

@@

%----------------------------------------------------------------------------------------
\subsection{ILP on the DWave}
\label{sec:methods:ILP-on-DWave}
%----------------------------------------------------------------------------------------
The minimal energy solution to Eq.~\eqref{eq:initial-ip-def} and Eq.~\eqref{eq:ilp-slack-bit-energy} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
Thus some knowledge of the problem is required.
In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large values of For $p$ increase the highest available energy of the system by multiples of $p$.
After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.
%----------------------------------------------------------------------------------------
\subsubsection{Minor Embedding}
\label{sec:methods:minor_embedding}
%----------------------------------------------------------------------------------------
Our proposed offset strategy is motivated by the structure of the Hamiltonian being evaluated by the annealer.
As a result, details of the embedding are important. We obtain an embedding for $G(n)$ with the \texttt{embed\_qubo} function provided by the DWave Oceans Python package~\cite{dwave_oceans} under the \texttt{dwave.embedding} module~\cite{2008arXiv0804.4884C}.
The same embedding is used for all DWave solves of the same graph (independent of offset), and consequently the simulation solves the resulting embedded Hamiltonian for $G(2)$.
Additionally, solving the same graph as a function of offset on the exact same qubits removes (or at least keeps consistent) the systematic effects due to solving a problem on different physical qubits.
We note that comparisons between different graphs in Fig.~\ref{fig:baseline} are subject to this uncontrolled systematic.

>>>>

As this mapping comes with a tunable parameter, such constraints can be lifted in a problem-specific manner to extend the applicability (Sec.~\ref{sec:methods:ilp-qubo-comments}).
Furthermore, the same algorithm can be extended to quadratic constraint optimization problems (Sec.~\ref{sec:methods:ilp:quadratic}).

@@

%----------------------------------------------------------------------------------------
\subsection{ILP on the DWave}
\label{sec:methods:ILP-on-DWave}
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
\subsubsection{Comment on ILP QUBO penalty term}
\label{sec:methods:ilp-qubo-comments}
%----------------------------------------------------------------------------------------

The minimal energy solution to Eq.~\eqref{eq:initial-ip-def} and Eq.~\eqref{eq:ilp-slack-bit-energy} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
Thus some knowledge of the problem is required.
In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large values of For $p$ increase the highest available energy of the system by multiples of $p$.
After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.
%----------------------------------------------------------------------------------------
\subsubsection{Minor Embedding}
\label{sec:methods:minor_embedding}
%----------------------------------------------------------------------------------------
Our proposed offset strategy is motivated by the structure of the Hamiltonian being evaluated by the annealer.
As a result, details of the embedding are important. We obtain an embedding for $G(n)$ with the \texttt{embed\_qubo} function provided by the DWave Oceans Python package~\cite{dwave_oceans} under the \texttt{dwave.embedding} module~\cite{2008arXiv0804.4884C}.
The same embedding is used for all DWave solves of the same graph (independent of offset), and consequently the simulation solves the resulting embedded Hamiltonian for $G(2)$.
Additionally, solving the same graph as a function of offset on the exact same qubits removes (or at least keeps consistent) the systematic effects due to solving a problem on different physical qubits.
We note that comparisons between different graphs in Fig.~\ref{fig:baseline} are subject to this uncontrolled systematic.
